% lerobot-bench --- 4-page arXiv writeup (cs.RO primary, cs.LG secondary).
% SCAFFOLD. Every \todo{...} is a placeholder for a number that lands
% from notebooks/01-write-finding.ipynb after the full sweep produces
% real parquet rows. Methodology and Related Work text is NOT a
% placeholder; it stays as-is and is the load-bearing content a HF
% Robotics reviewer reads.

\documentclass[10pt]{article}

\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.4ex plus .2ex minus .2ex}{0.6ex plus .2ex}
\titlespacing*{\subsection}{0pt}{1.0ex plus .2ex minus .2ex}{0.4ex plus .2ex}
\titlespacing*{\paragraph}{0pt}{0.4ex plus .1ex minus .1ex}{0.6em}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{url}

% --- \todo{...} renders as a high-visibility marker so future-you sees
% every unfilled placeholder. The macro is ONE line of red highlighter;
% no separate todonotes package, no margin clutter.
\newcommand{\todo}[1]{{\colorbox{red!20}{\textcolor{red!70!black}{\textbf{TODO:} #1}}}}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!50!black,
    citecolor=blue!50!black,
    urlcolor=blue!50!black,
}

\title{lerobot-bench: a multi-policy reproducible evaluation\\
suite for pretrained LeRobot policies}
\author{Th\'eo Hermann\\
\texttt{thermann.ai@gmail.com} \\
\texttt{https://github.com/thrmnn/lerobot-bench}}
\date{\today}

\begin{document}

\maketitle

% ---------------------------------------------------------------- %
% Abstract                                                         %
% ---------------------------------------------------------------- %

\begin{abstract}
Reported success rates for pretrained LeRobot~\cite{cadene2024lerobot}
policies live in self-reported tables across heterogeneous protocols,
with no shared seed accounting or confidence intervals. We introduce
\emph{lerobot-bench}, a public reproducible evaluation suite that runs
six policies --- four learned (Diffusion Policy, ACT, SmolVLA, XVLA)
and two weights-free baselines (no-op, uniform-random) --- on six
LeRobot sim envs (PushT, Aloha-transfer-cube, and the four LIBERO
suites~\cite{liu2023libero}), yielding 22~runnable
\textit{(policy, env)} cells under a multi-seed contract
(5~seeds $\times$ 50~episodes, $N{=}250$ binary outcomes). We report
Wilson and bootstrap 95\% CIs on every cell, paired comparisons with
explicit MDE bounds, and pin every policy entry to a fixed git
revision SHA so a parquet row is replayable bit-for-bit.
SmolVLA on LIBERO-10 measures 0.252~[0.202, 0.309], versus the
paper-reported 0.71 --- a gap that exceeds any plausible small-sample
artifact ($p{<}10^{-30}$) and which the shared protocol surfaces. The
implication is that single-seed published numbers from individual
policy papers should not be compared head-to-head without re-running
under a shared protocol --- and the protocol we ship is one such.
\end{abstract}

% ---------------------------------------------------------------- %
% Introduction                                                     %
% ---------------------------------------------------------------- %

\section{Introduction}

LeRobot~\cite{cadene2024lerobot} ships pretrained checkpoints for
Diffusion Policy~\cite{chi2023diffusion}, ACT~\cite{zhao2023learning},
SmolVLA~\cite{shukor2025smolvla}, XVLA~\cite{bu2025xvla}, and the
$\pi_0$ family~\cite{black2024pi0} across simulated manipulation envs.
Individual policy papers report success rates on these envs, but the
protocols differ in seed counts, episode budgets, success thresholds,
and how (or whether) CIs are derived --- a single-seed irreproducibility
trap documented in adjacent
fields~\cite{henderson2018deep,agarwal2021deep}.

We fill that gap with \emph{lerobot-bench}: open data (Hub dataset
\texttt{thrmnn/lerobot-bench-v1}, every per-episode outcome plus a
rollout MP4, indexed by \textit{(policy, env, seed, episode)}); open
eval (a pinned scriptable pipeline that re-derives any parquet row in
${<}1$\,h on commodity hardware, plus a resumable orchestrator); and
open analysis (\texttt{notebooks/01-write-finding.ipynb}, which
produces every table and figure here). The v1 roster is four learned
policies and two weights-free baselines crossed with six envs ---
22~runnable cells after the Hub-checkpoint filter; the $\pi_0$ family
is deferred to v1.1 for a host-RAM reason detailed in the Limitations.
The contribution is methodological as much as empirical: we ship the
seeding contract, the bootstrap protocol, and the MDE bound that
together make per-cell numbers bit-reproducible and CIs defensible
at $N{=}250$. The benchmark is the data; this paper is the defense.

% ---------------------------------------------------------------- %
% Related Work                                                     %
% ---------------------------------------------------------------- %

\section{Related work}
\label{sec:related}

\paragraph{Robot-learning benchmarks.}
PushT~\cite{chi2023diffusion} and the Aloha
suite~\cite{zhao2023learning} were each introduced as single-policy
harnesses; LIBERO~\cite{liu2023libero} ships four task suites
(\textit{spatial}, \textit{object}, \textit{goal}, \textit{long}; the
latter is exposed in lerobot as \texttt{libero\_10}) for compositional
generalisation. RLBench~\cite{james2020rlbench} and
CALVIN~\cite{mees2022calvin} provide larger task taxonomies but no
pretrained LeRobot-compatible checkpoints; Open
X-Embodiment~\cite{bohg2025open} provides training data, not an
evaluation protocol. None of the above ship a multi-policy
leaderboard with shared seed accounting, multi-seed CIs, and
re-runnable rows for the LeRobot policy stack.

\paragraph{Statistical rigor and floor baselines.}
We adopt the multi-seed bootstrap-CI prescription of Agarwal et
al.~\cite{agarwal2021deep}, motivated by the seed-fragility findings of
Henderson et al.~\cite{henderson2018deep}, and ship per-cell no-op and
uniform-random baselines (cf.\ OpenAI Gym~\cite{brockman2016openai}
convention) because LeRobot envs differ in how permissive their success
heuristics are --- the random floor is not a single number across the
matrix.

% ---------------------------------------------------------------- %
% Methods                                                          %
% ---------------------------------------------------------------- %

\section{Methods}
\label{sec:methods}

\paragraph{Sweep contract.}
The unit of evaluation is a \textit{cell}:
$(\text{policy}, \text{env}, \text{seed\_idx})$ with
$\text{seed\_idx} \in \{0,\ldots,4\}$. Each cell runs $n_\text{ep}{=}50$
episodes ($N{=}250$ binary outcomes) unless the auto-downscope rule
(below) reduces it. An episode runs from \texttt{env.reset(seed=$s$)}
until \texttt{terminated}, \texttt{truncated}, or env-specific
\texttt{max\_steps} (PushT 300, Aloha 400, LIBERO
$\in\{280,280,300,520\}$); success is the per-env standard reward
threshold (\texttt{config.SUCCESS\_REWARD}) at the final step.

\paragraph{Seeding contract.}
Per cell, numpy, torch, and CUDA generators are seeded with
$\text{seed}_\text{cell} = \text{seed\_idx} \cdot 1000$; the env is
reset per episode with $\text{seed}_\text{cell} + e$. Policy
stochasticity inherits the torch generator and is not re-seeded, so
the generator advances across episodes within a cell --- mid-cell
resume is therefore not bit-reproducible, and the orchestrator
(\texttt{checkpointing.plan\_resume}) re-runs partial cells from
$e{=}0$.

\paragraph{Per-cell CIs.}
We report $\hat{p} = (\text{successes})/N$ with the closed-form Wilson
score interval~\cite{wilson1927probable,agresti1998approximate} in the
leaderboard table and a percentile-bootstrap 95\%
interval~\cite{efron1979bootstrap, efron1993introduction}
($10{,}000$ resamples, seeded \texttt{Generator(42)}, resampling unit
is the \emph{episode}) for sanity-check and forest-plot display. The
two intervals agree to within 1\,pp at $N{=}250$ across the
$\hat{p}$ grid.

\paragraph{Paired comparisons across cells.}
For shared-protocol pairs we report paired $\Delta\hat{p}$ via paired
bootstrap (\texttt{stats.paired\_delta\_bootstrap}) and the two-sided
Wilcoxon signed-rank test~\cite{wilcoxon1945individual} on per-episode
differences (reducing in the limit to McNemar's
test~\cite{mcnemar1947note} for binary outcomes). Effect size is
Cohen's $h$~\cite{cohen1988statistical}; family-wise rate is
Bonferroni-controlled~\cite{bonferroni1936teoria} at $\alpha{=}0.05$
when more than one ranking claim per env is reported.

\paragraph{Minimum detectable effect.}
At $N{=}250$, Wilson 95\% half-width at $\hat{p}{=}0.5$ is
$\text{HW}{=}0.0615$, so $|\Delta\hat{p}|{<}0.1230$ is inconclusive
regardless of the bootstrap or Wilcoxon $p$-value
(\texttt{docs/MDE\_TABLE.md} tabulates the per-$\hat{p}$ threshold
and empirical paired-bootstrap MDE at $\rho \in \{0,0.3,0.5\}$). The
threshold shrinks for saturated cells (e.g.\ $0.0543$ at
$\hat{p}{=}0.95$). Deltas below it are reported as
\emph{inconclusive at $N{=}250$}, not as findings.

\paragraph{Auto-downscope rule.}
\label{sec:downscope}
Per-cell wall-clock budget is 3~hours on a single RTX~4060 laptop GPU
(8\,GB VRAM). After Day-0 calibration produces a per-policy mean step
latency $\overline{t}$ (ms/step),
\begin{equation}
    n_\text{ep} = \min\!\left(50,\ \left\lfloor
        \frac{3 \cdot 3600}{5 \cdot \texttt{env.max\_steps} \cdot
        \overline{t} / 1000} \right\rfloor\right).
\end{equation}
Only $n_\text{ep}$ shrinks (seeds fixed at five); a down-scoped cell
lands at $N{\in}\{50,100\}$, flagged in the leaderboard caption. Two
cells in v1 were down-scoped. Policies whose per-cell minimum
($N{=}50$) still exceeds budget are dropped, not silently truncated.

\paragraph{Sparse-matrix policy and reproducibility.}
A cell is N/A only when no public Hub checkpoint exists at lock-in
time; the $6{\times}6$ grid reduces to 22~runnable cells, with
sparsity shown as a visible gap (Table~\ref{tab:leaderboard}). Each
parquet row carries its code SHA, the lerobot version pin
(\texttt{lerobot==0.5.1}), and the SHA-256 of its rendered MP4; every
entry in \texttt{configs/policies.yaml} is locked to a fixed
\texttt{revision\_sha} (resolved 2026-05-03), and the eval loop
refuses to load a policy without one. A row is replayable with
\texttt{scripts/run\_one.py --policy P --env E --seed S}; the Hub
dataset \texttt{thrmnn/lerobot-bench-v1} is the data source for the
public Space and every figure below.

% ---------------------------------------------------------------- %
% Results                                                          %
% ---------------------------------------------------------------- %

\section{Results}
\label{sec:results}

\paragraph{Per-policy leaderboard.}
Table~\ref{tab:leaderboard} reports the pooled per-policy success
rate $\hat{p}$ across the envs each policy supports under
\texttt{env\_compat}, with the closed-form Wilson 95\% interval. Rows
with $N{<}250$ are auto-downscoped per Section~\ref{sec:downscope}
and flagged with $\dagger$. The full per-\textit{(policy, env)}
breakdown is Table~\ref{tab:breakdown}.

\begin{table}[h]
\centering
\small
\begin{tabular}{lrrrl}
\toprule
Policy & Envs & $N$ & $\hat{p}$ & 95\% CI (Wilson) \\
\midrule
ACT              & 1 & 250  & 0.824 & [0.772, 0.866] \\
Diffusion Policy & 1 & 125$\dagger$ & 0.816 & [0.739, 0.874] \\
SmolVLA          & 4 & 1000 & 0.621 & [0.591, 0.651] \\
random           & 6 & 1500 & 0.009 & [0.005, 0.015] \\
no-op            & 6 & 1500 & 0.000 & [0.000, 0.003] \\
\bottomrule
\end{tabular}
\caption{Pooled per-policy success rate with Wilson 95\% interval.
$\dagger$ marks the auto-downscoped diffusion\_policy${\times}$pusht
cell ($n_\text{ep}{=}25$, $N{=}125$). XVLA is excluded from the v1
leaderboard --- see the deferral paragraph below.}
\label{tab:leaderboard}
\end{table}

\begin{table}[h]
\centering
\small
\begin{tabular}{llrrl}
\toprule
Policy & Env & $N$ & $\hat{p}$ & 95\% CI (Wilson) \\
\midrule
ACT              & aloha\_transfer\_cube & 250 & 0.824 & [0.772, 0.866] \\
Diffusion Policy & pusht                 & 125$\dagger$ & 0.816 & [0.739, 0.874] \\
SmolVLA          & libero\_goal          & 250 & \textbf{0.928} & [0.889, 0.954] \\
SmolVLA          & libero\_spatial       & 250 & 0.776 & [0.720, 0.823] \\
SmolVLA          & libero\_object        & 250 & 0.528 & [0.466, 0.589] \\
SmolVLA          & libero\_10            & 250 & \textbf{0.252} & [0.202, 0.309] \\
random           & aloha\_transfer\_cube & 250 & 0.052 & [0.031, 0.087] \\
random           & all other envs        & 1250 & 0.000 & [0.000, 0.003] \\
no-op            & all envs              & 1500 & 0.000 & [0.000, 0.003] \\
\bottomrule
\end{tabular}
\caption{Per-\textit{(policy, env)} success rates, $N{=}5\cdot
n_\text{ep}$ binary outcomes per cell. $\dagger$: auto-downscoped to
$n_\text{ep}{=}25$ per Section~\ref{sec:downscope}. \texttt{random}
on \texttt{aloha\_transfer\_cube} is the only above-floor baseline
--- the \texttt{gym-aloha} success heuristic is the most permissive
of the matrix. The MDE band at $N{=}250$, $\hat{p}{=}0.5$ is $0.123$.
22~runnable cells in total; XVLA cells deferred (see below).}
\label{tab:breakdown}
\end{table}

\paragraph{Headline finding: SmolVLA on LIBERO-10 measures 0.252,
not the paper-reported 0.71.}
SmolVLA's pooled rate across the four LIBERO suites is
0.621~[0.591, 0.651]. The per-suite breakdown reveals this average
hides a sharp gradient: 0.928~[0.889, 0.954] on
\texttt{libero\_goal} and 0.776~[0.720, 0.823] on
\texttt{libero\_spatial} are within reach of the SmolVLA-0.45B
numbers reported by Shukor et al.~\cite{shukor2025smolvla}
(0.92, 0.90 respectively), but \texttt{libero\_object} lands at
0.528~[0.466, 0.589] (paper 0.96) and \texttt{libero\_10} at
0.252~[0.202, 0.309] (paper 0.71) --- a $35\%$ relative ratio on
the long-horizon suite. The Wilson half-width on the
\texttt{libero\_10} cell is $0.054$ at $N{=}250$, so the gap is not
a small-sample artifact: a binomial sample whose true rate equals
the paper-reported 0.71 produces $\hat{p}\leq 0.31$ with probability
below $10^{-30}$. We caught and ruled out one mundane source of
divergence (the act${\times}$aloha cell was re-run after PR~\#51
fixed a postprocessor wiring bug; the SmolVLA loader has been
exercised on three suites with no analogous bug surfacing), so the
gap is not a loader bug we can name. Two hypotheses we cannot
distinguish from public information: (a) the SmolVLA-0.45B Hub
checkpoint generalises less well to the 10-task long-horizon variant
than the paper's reported numbers imply, possibly because of the
checkpoint scale or training-time task-set overlap; or
(b)~the LIBERO evaluation protocol in the SmolVLA paper differs from
the LeRobot \texttt{env.LIBEROEnv}{+}\texttt{task\_id=0} protocol we
ship (success threshold, success-trigger horizon, or task selection).
We report the gap and the hypotheses; deciding between them is
out of scope for a sim screening protocol and is the kind of
multi-policy comparable result lerobot-bench exists to surface.

\paragraph{SmolVLA${\times}$libero\_object shows a deterministic
ceiling.} On \texttt{libero\_object}, the across-seed variance of the
seed-level success rates is $1{\times}10^{-4}$ --- the five seeds
agree on $\hat{p}{=}0.528$ to within a single episode. The other
SmolVLA${\times}$LIBERO cells show variance two to forty times
higher (e.g.\ $5.9{\times}10^{-3}$ on \texttt{libero\_spatial},
$2.7{\times}10^{-3}$ on \texttt{libero\_10}). The
\texttt{libero\_object} failure mode is therefore consistent across
seeds rather than stochastic, suggesting a specific subset of object
configurations the checkpoint cannot solve regardless of the rollout
randomness --- a structural cap, not a sample-size problem. This is
the kind of signal the failure-mode taxonomy
(Section~\ref{sec:taxonomy}) is meant to localise.

\paragraph{Baseline sanity.}
The no-op baseline succeeds zero times across all six envs
($N{=}1500$, Wilson upper bound $0.003$). The uniform-random
baseline succeeds zero times on \texttt{pusht} and on every LIBERO
suite, and is the only baseline above floor on
\texttt{aloha\_transfer\_cube} ($\hat{p}{=}0.052$,
[0.031, 0.087]) where the \texttt{gym-aloha} cube-transfer success
heuristic is the most permissive in the matrix. The baseline floor
is therefore not a single number across the leaderboard, which is
exactly why we run it on every cell rather than reporting it once.

\paragraph{XVLA deferral.}
\texttt{xvla\_libero} was executed across all four LIBERO suites
(875~episodes total) but is \textbf{deferred from the v1 leaderboard}.
Two Hub-artifact wiring bugs (missing rotation-6D$\to$axis-angle
post-processor; missing ImageNet normalization) were patched in the
loader (PR~\#71, \#74), yet a third unresolved issue produced 0/40 in
a post-patch sanity sweep (Wilson upper bound $0.088$ at $N{=}40$,
consistent with a non-functional load). The deferral, patched bugs,
and unresolved issue are in \texttt{docs/DEFERRED\_POLICIES.md}; an
upstream issue against \texttt{huggingface/lerobot} is in flight. XVLA
returns to the matrix in v1.1.

\paragraph{Stats sanity.}
Wilson and pivotal-bootstrap 95\% CIs agree to within one Wilson
half-width on every cell (notebook cell~11); no cell triggers the
disagreement flag. The orchestrator advanced through 13 distinct
\texttt{code\_sha} values across the 110 \textit{(policy, env, seed)}
cells, with policy revision pins and \texttt{lerobot\_bench.stats}
helpers held constant --- noted as a Limitation, not a confound;
every parquet row carries its originating SHA.

\paragraph{Failure-mode taxonomy.}
\label{sec:taxonomy}
We hand-label 5--10 failed rollouts per cell into six modes
(trajectory overshoot, gripper slip, timeout, wrong object, premature
release, drift; definitions and labeling protocol in
\texttt{docs/FAILURE\_TAXONOMY.md}). Each rollout takes the first mode
that fits in chronological order so per-cell counts sum to the failure
total; failures are stratified across seeds (one per seed) so a single
bad seed cannot dominate. The companion bar chart lives on the public
Space (\texttt{thrmnn/lerobot-bench-v1}).

% ---------------------------------------------------------------- %
% Discussion                                                       %
% ---------------------------------------------------------------- %

\section{Discussion}

\paragraph{What the leaderboard says.}
The headline gap on SmolVLA${\times}$\texttt{libero\_10}
(Section~\ref{sec:results}) is the kind of result that motivates the
benchmark: a single planned paper-vs-measured comparison, clearing the
per-cell MDE by an order of magnitude under a shared protocol, exposes
a discrepancy no single-policy paper could have surfaced. The
contribution is the protocol that makes such discrepancies legible,
not a new ranking claim --- and the per-policy table stands as the
reference for future work onboarding new checkpoints.

\subsection{Limitations}

We list the three most load-bearing limitations; the full list
(simulation-vs-real gap, single-hardware ms/step bias, episode-budget
MDE ceiling) is in \texttt{docs/LIMITATIONS.md}.

\begin{itemize}\setlength{\itemsep}{2pt}
    \item \textbf{Host-RAM cold-load excludes the $\boldsymbol{\pi_0}$
    family in v1.} The $\pi_0$, $\pi_0$-FAST, and $\pi_{0.5}$
    checkpoints (PaliGemma-3B backbone) require ${\sim}30$\,GB of host
    CPU RAM during cold load --- not from steady-state activations
    ($<\,4$\,GB peak VRAM), but from \texttt{from\_pretrained}
    weight-conversion staging buffers. The 32\,GB WSL2 laptop used for
    v1 lacks headroom; quantized weights or
    \texttt{accelerate}'s \texttt{device\_map="auto"} streaming load
    should bring this under 12\,GB in v1.1. v1 therefore compares four
    learned policies, not the originally targeted seven.
    \item \textbf{Sparse matrix coverage.} A cell is N/A only when no
    public Hub checkpoint exists, so cross-policy comparisons are valid
    only within shared envs. The single multi-policy block in v1 is the
    four LIBERO suites, shared by SmolVLA and XVLA (deferred above);
    PushT and Aloha each carry one learned policy plus the two
    baselines.
    \item \textbf{Multi-comparison concerns.} Any pair not
    pre-registered as a planned comparison is exploratory. The headline
    finding (SmolVLA${\times}$\texttt{libero\_10}, a single planned
    paper-vs-measured comparison) clears the MDE band by an order of
    magnitude; cross-policy paired tests on shared envs are deferred to
    v1.1 when XVLA returns to the matrix.
\end{itemize}

\subsection{Future work}

v1.1 onboards the $\pi_0$ family (quantized or \texttt{accelerate}
streaming load, per Limitations), returns XVLA to the matrix, and
adds the remaining LIBERO task variants (v1 locks
\texttt{task\_id=0}). New policies onboard via a single PR adding a row
to \texttt{configs/policies.yaml}. A hardware re-run with the
sim-to-real bridge of choice is the natural follow-up.

% ---------------------------------------------------------------- %
% References                                                       %
% ---------------------------------------------------------------- %

{\footnotesize
\linespread{0.96}\selectfont
\let\oldthebibliography\thebibliography
\renewcommand{\thebibliography}[1]{%
  \oldthebibliography{#1}%
  \setlength{\itemsep}{0pt}\setlength{\parsep}{0pt}}
\bibliographystyle{plain}
\bibliography{references}
}

\end{document}
